Distribution-oblivious Programming with Dish

### 2019-10-03 pldi/draft.tex
Update intro

To understand this contrast, consider calculating term frequencies over a set of input files.
For a user with \emph{one} computer, this is achievable with a short \unix pipeline~\cite{bentley1986literate}:

@@

Combining several features, Unix makes small tasks easy to express:
  $p_1$ creates a character stream, breaks it down to words, transliterates them lower-case, sorts them to group duplicates, counts and replaces duplicates, sorts them numerically and in reverse order, picks the top five results and writes them to a file \ttt{out}.
% composition allows the composition of general primitives
Key elements of \unix are the ability to compose programs written in different languages, the abstraction of a file system as a set of resident streams, a small but extensible library of commands, and the ability to resolve names within a global context.
Under the hood, the \unix kernel buffers results, synchronizes processing stages, and generally orchestrates the computation.

@@

For a user with many computers, however, rewriting this pipeline to exploit distribution requires a significant cost in terms of manual effort.
% The scope of such rewrites, and therefore the cost of manual effort, can vary considerably.
Such cost is at best moderate when pipelines can be expressed in domain-specific frameworks---for example, Hadoop and Spark provide a few purely functional primitives that 
As long as the program fits into the model this is only moderately difficult;
For simple, one-off pipelines that take a few minutes to compose this cost---order of magnitude higher than---becomes unjustifiable.

>>>>

To understand this sharp contrast, consider calculating term frequencies over a set of input files:

@@

Combining several features, \unix makes small tasks easy to express:
  $p_1$ creates a character stream, breaks it down to words, transliterates them lower-case, sorts them to group duplicates, counts and replaces duplicates, sorts them numerically and in reverse order, picks the top five results and writes them to a file \ttt{out}.
For a user with \emph{one} computer and small input, this pipeline takes a few seconds to compose and execute~\cite{bentley1986literate}.
% composition allows the composition of general primitives

@@

For a user with many computers and larger inputs, however, developing $p_1$'s distributed equivalent requires a significant effort.
% The scope of such rewrites, and therefore the cost of manual effort, can vary considerably.
Such cost is at best moderate when pipelines can be expressed in domain-specific frameworks---for example, Hadoop and Spark provide a few purely functional primitives that 
As long as the program fits into the model this is only moderately difficult;
For simple, one-off pipelines that take a few minutes to compose this cost---order of magnitude higher than---becomes unjustifiable.
